Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-31 experiments.tex
Halloween camera-ready

Processor hardware parameters are directly related to the VLIW core
and includes the size of the register files and the number of
functional units of each type. On the software side, a set of the most
impacting code compilation parameters has been selected.
Table~\ref{tab:param} show the complete set of parameters included in
the design space and their possible values. The total size of design
space, which grows with the product of parameter cardinalities is
about $1.33 \times 10^{14}$.

@@

Although an analogy between the concepts of ``era'' and ``generation''
can be considered, comparisons have been carried out using as
reference a fixed amount of total unique simulations, instead of a given
number of eras/generations . The purpose is to make the comparison
fair and accurate from the algorithm performance perspective, since a fixed budget of
different simulations is more directly related to the actual amount of time
required to execute the exploration; on the other side, simply
referring to a given number of generations/eras could be inaccurate
when a considerable number of configurations remain unaltered in the
current population (e.g. because of a local optimum)\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.

>>>>

Processor hardware parameters are directly related to the VLIW core
and includes the size of the register files and the number of
functional units of each type. On the software side, a set of the most
impacting code compilation parameters has been selected.
Table~\ref{tab:param} show the complete set of parameters included in
the design space and their possible values. The total size of design
space, which grows with the product of parameter cardinalities, is
about $1.33 \times 10^{14}$.

@@

Although an analogy between the concepts of ``era'' and ``generation''
can be considered, comparisons have been carried out using as
reference a fixed amount of total unique simulations, instead of a given
number of eras/generations . The purpose is to make the comparison
fair and accurate from the algorithm performance perspective, since a fixed budget of
different simulations is more directly related to the actual amount of time
required to execute the exploration.
%; on the other side, simply
%referring to a given number of generations/eras could be inaccurate
%when a considerable number of configurations remain unaltered in the
%current population (e.g. because of a local optimum)
\comment{AA: Da 'on the other side' fin qui non ho capito cosa vuoi dire}.
\comment{DAV: se non lo capisci vuol dire che o e' scritto male o e'
inutile, per adesso lo tolgo.}
